Characterizing Execution Times on Realistic Programs

### 2018-03-29 pt_characterization/real_data/paper.tex
New draft

\subsection{Insertion sort~\label{sec:sort}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements.

Figures~\ref{fig:sort1} and ~\ref{fig:sort2} exhibit 
histograms of the execution times measured on the same insertion sort program as 
the input size grows from 100K to 1,160K elements.% by the steps of 2x. 
Note that we used one standard deviation in Figure~\ref{fig:sort400_dist} as
a couple of outliers, which were not eliminated by the original protocol, 
resulted in disturbing the rendering of a clean distribution.

\begin{figure}[h]
	\centering
%	\subfigure[PT frequency on SORT25]{
%		\includegraphics[scale=0.43]{sort25_dist.eps}
%		\label{fig:sort25_dist}
%	}
%	\subfigure[PT frequency on SORT50]{
%		\includegraphics[scale=0.43]{sort50_dist.eps}
%		\label{fig:sort50_dist}
%	}
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT144]{
		\includegraphics[scale=0.43]{sort144_dist.eps}
		\label{fig:sort144_dist}
	}
	\subfigure[PT frequency on SORT200]{
		\includegraphics[scale=0.43]{sort200_dist.eps}
		\label{fig:sort200_dist}
	}
	\subfigure[PT frequency on SORT288]{
		\includegraphics[scale=0.43]{sort288_dist.eps}
		\label{fig:sort288_dist}
	}
	\caption{PT Histograms of SORT25 ... SORT288~\label{fig:sort1}}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT580]{
		\includegraphics[scale=0.43]{sort580_dist.eps}
		\label{fig:sort588_dist}
	}
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\subfigure[PT frequency on SORT1000]{
		\includegraphics[scale=0.43]{sort1000_dist.eps}
		\label{fig:sort1000_dist}
	}
	\caption{PT Histograms of SORT400 ... SORT1000~\label{fig:sort2}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT1160]{
		\includegraphics[scale=0.43]{sort1160_dist.eps}
		\label{fig:sort1160_dist}
	}
	\subfigure[PT frequency on SORT2320 (not complete)]{
		\includegraphics[scale=0.43]{sort2320_dist.eps}
		\label{fig:sort2320_dist}
	}
	\caption{PT Histograms of SORT1160 ... SORT2320~\label{fig:sort3}}
\end{figure}

>>>>

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of insertion sort and INC (a nested-for-loop) programs. 
The insertion sort program 
sorts the elements of a given array in non-decreasing order.  
The program repeatedly runs 300 times for a given input size. 
The input size for the program varies from 144K to 344K integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
An INC program's task length is correspondingly determined by the program time 
of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program.

%
%Figures~\ref{fig:sort1} and ~\ref{fig:sort2} exhibit 
%histograms of the execution times measured on the same insertion sort program as 
%the input size grows from 100K to 1,160K elements.% by the steps of 2x. 
%Note that we used one standard deviation in Figure~\ref{fig:sort400_dist} as
%a couple of outliers, which were not eliminated by the original protocol, 
%resulted in disturbing the rendering of a clean distribution.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT144]{
		\includegraphics[scale=0.43]{sort144_dist.eps}
		\label{fig:sort144_dist}
	}	
	\subfigure[PT frequency on INC8.8]{
		\includegraphics[scale=0.43]{inc8.8_dist.eps}
		\label{fig:inc8.8_dist}
	}
	\subfigure[PT frequency on SORT177]{
		\includegraphics[scale=0.43]{sort177_dist.eps}
		\label{fig:sort177_dist}
	}	
	\subfigure[PT frequency on INC13]{
		\includegraphics[scale=0.43]{inc13.0_dist.eps}
		\label{fig:inc13_dist}
	}
	\caption{PT Histograms I~\label{fig:sort1}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT144]{
		\includegraphics[scale=0.43]{sort244_dist.eps}
		\label{fig:sort144_dist}
	}	
	\subfigure[PT frequency on INC25.8]{
		\includegraphics[scale=0.43]{inc25.8_dist.eps}
		\label{fig:inc25.8_dist}
	}
	\subfigure[PT frequency on SORT288]{
		\includegraphics[scale=0.43]{sort177_dist.eps}
		\label{fig:sort177_dist}
	}	
	\subfigure[PT frequency on INC35]{
		\includegraphics[scale=0.43]{inc13.0_dist.eps}
		\label{fig:inc35_dist}
	}
	\caption{PT Histogram Comparison II~\label{fig:sort2}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT344]{
		\includegraphics[scale=0.43]{sort344_dist.eps}
		\label{fig:sort344_dist}
	}	
	\subfigure[PT frequency on INC51.5]{
		\includegraphics[scale=0.43]{inc51.5_dist.eps}
		\label{fig:inc51.5_dist}
	}
	\caption{PT Histogram Comparison III~\label{fig:sort3}}
\end{figure}

@@

\section{Additional Insertion Sort~\label{sec:add_new}}

\begin{figure}[h]
	\centering
%	\subfigure[PT frequency on SORT25]{
%		\includegraphics[scale=0.43]{sort25_dist.eps}
%		\label{fig:sort25_dist}
%	}
%	\subfigure[PT frequency on SORT50]{
%		\includegraphics[scale=0.43]{sort50_dist.eps}
%		\label{fig:sort50_dist}
%	}
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT580]{
		\includegraphics[scale=0.43]{sort580_dist.eps}
		\label{fig:sort588_dist}
	}
	\caption{PT Histograms of SORT100 ... SORT580~\label{fig:n_sort1}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\subfigure[PT frequency on SORT1000]{
		\includegraphics[scale=0.43]{sort1000_dist.eps}
		\label{fig:sort1000_dist}
	}
	\subfigure[PT frequency on SORT1160]{
		\includegraphics[scale=0.43]{sort1160_dist.eps}
		\label{fig:sort1160_dist}
	}
	\subfigure[PT frequency on SORT2320 (not complete)]{
		\includegraphics[scale=0.43]{sort2320_dist.eps}
		\label{fig:sort2320_dist}
	}
	\caption{PT Histograms of SORT800 ... SORT2320~\label{fig:n_sort2}}
\end{figure}

%\subsection{Insertion sort~\label{sec:sort}} 
%This section shows a series of histograms of an insertion sorting program that 
%sorts the elements of a given array in non-decreasing order. 
%The program repeatedly runs 300 times for a given input size. 
%The input size for the program 
%varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
%Note that each sort program over a specific input size is termed SORT{\it x}: 
%for instance, SORT100 indicates the insertion sort program over 100K elements. 
%
%Figures~\ref{fig:sort1} and ~\ref{fig:sort2} exhibit 
%histograms of the execution times measured on the same insertion sort program as 
%the input size grows from 100K to 1,160K elements.% by the steps of 2x. 
%Note that we used one standard deviation in Figure~\ref{fig:sort400_dist} as
%a couple of outliers, which were not eliminated by the original protocol, 
%resulted in disturbing the rendering of a clean distribution. 
%
%\begin{figure}[h]
%	\centering
%%	\subfigure[PT frequency on SORT25]{
%%		\includegraphics[scale=0.43]{sort25_dist.eps}
%%		\label{fig:sort25_dist}
%%	}
%%	\subfigure[PT frequency on SORT50]{
%%		\includegraphics[scale=0.43]{sort50_dist.eps}
%%		\label{fig:sort50_dist}
%%	}
%	\subfigure[PT frequency on SORT100]{
%		\includegraphics[scale=0.43]{sort100_dist.eps}
%		\label{fig:sort100_dist}
%	}
%	\subfigure[PT frequency on SORT144]{
%		\includegraphics[scale=0.43]{sort144_dist.eps}
%		\label{fig:sort144_dist}
%	}
%	\subfigure[PT frequency on SORT200]{
%		\includegraphics[scale=0.43]{sort200_dist.eps}
%		\label{fig:sort200_dist}
%	}
%	\subfigure[PT frequency on SORT288]{
%		\includegraphics[scale=0.43]{sort288_dist.eps}
%		\label{fig:sort288_dist}
%	}
%	\caption{PT Histograms of SORT25 ... SORT288~\label{fig:sort1}}
%\end{figure}
%
%\clearpage
%\pagebreak
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on SORT400]{
%		\includegraphics[scale=0.43]{sort400_dist.eps}
%		\label{fig:sort400_dist}
%	}
%	\subfigure[PT frequency on SORT580]{
%		\includegraphics[scale=0.43]{sort580_dist.eps}
%		\label{fig:sort588_dist}
%	}
%	\subfigure[PT frequency on SORT800]{
%		\includegraphics[scale=0.43]{sort800_dist.eps}
%		\label{fig:sort800_dist}
%	}
%	\subfigure[PT frequency on SORT1000]{
%		\includegraphics[scale=0.43]{sort1000_dist.eps}
%		\label{fig:sort1000_dist}
%	}
%	\caption{PT Histograms of SORT400 ... SORT1000~\label{fig:sort2}}
%\end{figure}
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on SORT1160]{
%		\includegraphics[scale=0.43]{sort1160_dist.eps}
%		\label{fig:sort1160_dist}
%	}
%	\subfigure[PT frequency on SORT2320 (not complete)]{
%		\includegraphics[scale=0.43]{sort2320_dist.eps}
%		\label{fig:sort2320_dist}
%	}
%	\caption{PT Histograms of SORT1160 ... SORT2320~\label{fig:sort3}}
%\end{figure}
